Automated Assessment of Residual Plots with Computer Vision Models

### 2025-07-29 paper.tex
Revert main paper back to commit #4b6fdd, and compile all files
Recompile

{\centering \includegraphics[width=1\linewidth]{paper_files/figure-latex/cnn-diag-1}

@@

These \texttt{R} packages were used for the work: \texttt{tidyverse}
\citep{tidyverse}, \texttt{lmtest} \citep{lmtest}, \texttt{mpoly}
\citep{mpoly}, \texttt{ggmosaic} \citep{ggmosaic}, \texttt{kableExtra}
\citep{kableextra}, \texttt{patchwork} \citep{patchwork},
\texttt{rcartocolor} \citep{rcartocolor}, \texttt{glue} \citep{glue},
\texttt{ggpcp} \citep{ggpcp}, \texttt{here} \citep{here},
\texttt{magick} \citep{magick}, and \texttt{reticulate}
\citep{reticulate}.

@@

>>>>

{\centering \includegraphics[width=1\linewidth]{figures/cnn}

@@

These \texttt{R} packages were used for the work: \texttt{tidyverse}
\citep{tidyverse}, \texttt{lmtest} \citep{lmtest}, \texttt{mpoly}
\citep{mpoly}, \texttt{ggmosaic} \citep{ggmosaic}, \texttt{kableExtra}
\citep{kableextra}, \texttt{patchwork} \citep{patchwork}, \texttt{glue}
\citep{glue}, \texttt{ggpcp} \citep{ggpcp}, \texttt{here} \citep{here},
and \texttt{reticulate} \citep{reticulate}.

@@

\section*{Data Availability
Statement}\label{data-availability-statement}
\addcontentsline{toc}{section}{Data Availability Statement}

The data that support the findings of this study are openly available in
the project's GitHub repository
(\url{https://github.com/TengMCing/auto_residual_reading_paper}).
